  
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[colorinlistoftodos]{todonotes}
\pagestyle{empty}

\title{Stable Matching Report}
\author{Jessica Lundmark and Tilde Höst}

\begin{document}
  \maketitle

  \section{Results}

  \todo[inline]{Briefly comment the results, did the script say all your solutions were correct? Approximately how long time does it take for the program to run on the largest input? What takes the majority of the time?}
  The script says that the solution is correct. The program runs at about 14 to 15 seconds (high to low 1400's milliseconds). The GS algorithms accounts for 40-50ms of this time, and the rest of the time is just parsing the input.

  \section{Implementation details}

  \todo[inline]{How did you implement the solution? Which data structures were used? Which modifications to these data structures were used? What is the overall running time? Why?}
  
  The program consists of java classes for Man, Woman, Couple, Solution and a Main.java (that just creates a solution object and calls solution.run()). The main parsing takes place in the Solution class, although the women invert their preference lists on their own when they are initialized. 
  \newline
  Women are stored in a (hash)map of name=woman for O(1) access to her.
  Couples are stored in a (hash)map of woman=couple for O(1) access to all people involved (the womans' "singleness" is a boolean that can be called).
  Men are stored in a linkedlist, as are their preferences. Adding and removing at end and start has O(1). 
The structures used guarantee that all method calls within the Gale Shapley algorithm are O(1) and therefore the GSA running time would be assumed to be O($n^2$), due to the while loop that in a worst case scenario will run N times N times.
  
  Parsing running time would be high, due to instances as the createWomen() method, where I have used nested for-loops, O($n^2$), and it will run $n^2$ times in at least two places.
  
  

\end{document}